This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-07 article.tex
-\relax- instead of -- to prevent an en-dash
Fixed the bottom of Kolskaya from being cut off

Although not entirely required to understand the polyglot, I think it
is useful to describe the git packfile format here, since it is not
well documented elsewhere. If that doesn't interest you, it's safe to
skip to the next section.  But if you do proceed, I hope you like
Soviet holes, dear neighbor, because chasing this rabbit might remind
you of \includegraphics{kolskaya}.

@@

Getting the object to be compressed with zero compression is also
relatively easy.  That's because git was built in almost religious
adherence to The UNIX Philosophy: It is architected with hundreds of
sub commands it calls ``plumbing,'' of which the vast majority you
will likely have never heard. For example, you might be aware
that \texttt{git pull} is equivalent to a \texttt{git fetch} followed
by a \texttt{git merge}. In fact, the \texttt{pull} code actually
spawns a new \texttt{git} child process to execute each of those
subcommands. Likewise, the \texttt{git bundle} command spawns
a \texttt{git pack-objects} child process to generate the packfile
portion of the bundle.  All we need to do is inject
the \texttt{--compression=0} argument into the list of command line
arguments passed to \texttt{pack-objects}.  This is a one-line
addition to \texttt{bundle.c}:\\ {\footnotesize {\color{gray}
\verb|    argv_array_pushl(&pack_objects.args,|\\
\verb|                     "pack-objects", "--all-progress-implied",|}\\
\verb|                     "--compression=0",|\\
{\color{gray}
\verb|                     "--stdout", "--thin", "--delta-base-offset",|\\
\verb|                     NULL);|
}}

>>>>

Although not entirely required to understand the polyglot, I think it
is useful to describe the git packfile format here, since it is not
well documented elsewhere. If that doesn't interest you, it's safe to
skip to the next section.  But if you do proceed, I hope you like
Soviet holes, dear neighbor, because chasing this rabbit might remind
you of \raisebox{-0.5pt}{\includegraphics{kolskaya}}.

@@

Getting the object to be compressed with zero compression is also
relatively easy.  That's because git was built in almost religious
adherence to The UNIX Philosophy: It is architected with hundreds of
sub commands it calls ``plumbing,'' of which the vast majority you
will likely have never heard. For example, you might be aware
that \texttt{git pull} is equivalent to a \texttt{git fetch} followed
by a \texttt{git merge}. In fact, the \texttt{pull} code actually
spawns a new \texttt{git} child process to execute each of those
subcommands. Likewise, the \texttt{git bundle} command spawns
a \texttt{git pack-objects} child process to generate the packfile
portion of the bundle.  All we need to do is inject
the \texttt{-\relax-compression=0} argument into the list of command line
arguments passed to \texttt{pack-objects}.  This is a one-line
addition to \texttt{bundle.c}:\\ {\footnotesize {\color{gray}
\verb|    argv_array_pushl(&pack_objects.args,|\\
\verb|                     "pack-objects", "--all-progress-implied",|}\\
\verb|                     "--compression=0",|\\
{\color{gray}
\verb|                     "--stdout", "--thin", "--delta-base-offset",|\\
\verb|                     NULL);|
}}
